---
title: "Penguin Data"
format: html
editor: visual
---

```{r include = FALSE}
#install.packages("palmerpenguins")
library(palmerpenguins)
library(tidyverse)
```

## Data

The data I am working with includes data (like flipper length, bill length, and bill depth) from 344 penguins. The penguins in this dataset are from 3 different species, and the data was collected from 3 islands.

![](https://www.thoughtco.com/thmb/DXL0rwztfCOpWKXmGD_cNheS1uQ=/1500x0/filters:no_upscale():max_bytes(150000):strip_icc()/149267744-56a008755f9b58eba4ae8f46.jpg){width="318"}

## Single trait distribution

These charts show the distribution in bill lengths of different species of penguins.

```{r echo = FALSE, message=FALSE, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, fill = species)) +
  geom_histogram(binwidth = 1) +
  facet_wrap(~species, nrow = 3)
```

```{r echo = FALSE, message=FALSE, warning=FALSE}
penguins %>%
  ggplot() +
  geom_density(mapping = aes(x = bill_length_mm, fill=species), alpha=0.5)
```

## Relationship between multiple traits

These charts show the relationship between body mass and flipper length in the different species of penguins.

```{R echo = FALSE, message=FALSE, warning=FALSE}
ggplot(penguins, aes(x = body_mass_g, y = flipper_length_mm, color = species)) +
  geom_point() +
  geom_smooth(method="lm")

```

## Sexual dimorphism

These charts show which traits are sexually dimorphic and which are not.

```{r echo = FALSE, message=FALSE, warning=FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = bill_depth_mm, color = sex)) +
  geom_point(size = 1) +
  facet_wrap(~species)

```


